Reaching is Better When You Get What You Want: Realtime Feedback of Intended Reaching Trajectory Despite an Unstable Environment

### 2015-05-29 Paper2frontiers/frontiers.tex
updated with tejas

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Horowitz {et~al.}} %use et al only if is more than 1 author
\def\Authors{Justin Horowitz\,$^1$, Co-Author\,$^{2}$ and Co-Author\,$^{2,*}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Laboratory X, Institute X, Department X, Organization X, City X , State XX (only USA, Canada and Australia), Country X \\
$^{2}$Laboratory X, Institute X, Department X, Organization X, City X , State XX (only USA, Canada and Australia), Country X  }
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{James Patton}
\def\corrAddress{Laboratory X, Institute X, Department X, Organization X, Street X, City X , State XX (only USA, Canada and Australia), Zip Code, X Country X}
\def\corrEmail{pattonj@uic.edu}

@@

In contrast, displaying anything other than what truthfully happens is a distortion and a lie. Like many other visual distortion experiments \citep{miles1980long, pine1996learning}, intent feedback (IF) introduces a visuomotor discrepancy that may be confusing to the nervous system. Preplanning a specific route may not necessary, and instead the system might continuously react to the environmental disturbances until it reaches the goal. If people try to achieve a goal while minimizing some measure of cost, it is possible to compute a set of rules for reacting to the environment without a specific intended route using optimal feedback control\citep{todorov2002optimal}. While this modeling strategy has been very successful at explaining data, it fundamentally assumes that corrective actions will be taken in response to relevant disturbances. Goals can also be reached at minimal \textit{expected} cost by constructing -- and possibly updating -- a specific intended route. IF may be troublesome if the nervous system cannot recognize it because no particular trajectory was intended.

@@

\subsection{Intent Extraction}
The well-known motion control structure of Shadmehr and Mussa-Ivaldi\cite{shadmehr1994adaptive} relates arm trajectory, $q$, to desired arm trajectory, $q_d$, and any external disturbance, $E$ using physical parameters of the arm. To show how this model can be algebraically inverted to instead describe desired arm trajectory as a function of arm trajectory and external disturbance, we write it as a torque balance:
\begin{equation}
\underbrace{\overbrace{M(q)\ddot{q}}^{\text{Inertia}}+\overbrace{G(q,\dot{q})}^{\text{Coriolis, Centripal}}}_{\text{Plant}}+E=
\underbrace{\overbrace{\tau_{ff}}^{\text{Feedforward}}+\overbrace{\tau_{fb}}^{\text{Feedback}}}_\text{Controller}
\end{equation}
Where $M$ is the mass matrix, $q$ is the joint angles, $\dot{q}$ is joint angular velocities, $\ddot{q}$ is joint angular accelerations, and $G$ contains both Coriolis and centripetal effects. Typical applications solve this torque balance for $\ddot{q}$ and use a numerical differential equation solver to predict arm trajectory in the context of a disturbance of interest, a feedback model, and feedforward torques determined by inverse dynamics. Rather than test hypotheses regarding the learning, production, or composition of this feedforward torque, we instead solve for it:
\begin{equation}
\tau_{ff}=M(q)\ddot{q}+G(q,\dot{q})+E-\tau_{fb}
\end{equation}
Then we note that feedforward torque can have a one-to-one correspondence with desired acceleration, $\ddot{q}_d$:
\begin{equation}
\hat{M}(q_d)\ddot{q}_d+\hat{G}(q_d,\dot{q}_d)+\hat{E}=\tau_{ff}
\end{equation}
Hats ( $\hat{}$ ) denote the nervous system's best estimate of a physical quantity. Combining these expressions, suppressing state dependencies, and solving for $\ddot{q}_d$:
\begin{equation}
\ddot{q}_d=\hat{M}^{-1} \{M\ddot{q}+G-\hat{G}+E-\hat{E}-\tau_{fb}\}
\end{equation}
In this form, a differential equation solver can determine $q_d$ as it evolves in time if a few assumptions are made and conditions are met. First, $\hat{E}$ must be modeled or assumed, so we choose $\hat{E}=0$. In the presence of a zero mean white noise force disturbance its mean should be zero, but it is unlikely to be exactly zero and may reflect an average of only the last few exposures\citep{scheidt2001learning}. Next, the matrix $\hat{M}(q_d)$ must be invertible, but we can ensure this through our choice of workspace. Finally, feedback torque requires a model of arm impedance, which is known to be task-dependent\citep{gomi1998task} and may vary over the course of a reach\citep{niu2010temporal}. With no prior knowledge of arm impedance for this task-disturbance combination, we presumed the feedback torque model of Shadmehr and Mussa-Ivaldi anticipating that it is sufficiently accurate or easy to learn (experiment 1). The experiment was repeated with a lower stiffness estimate (experiment 2) to explore any dependence on this assumption.

@@

\begin{figure}[h]
\centering
\framebox{\parbox{3in}{\includegraphics{Yplots.eps}
}}
\caption{Typical subjects made center-out targeted reaching motions under experimentally varied force and feedback conditions. Subjects used feedback of either hand motions (black lines) or estimated intent (red lines) to complete these reaches. Intent was estimated using either the stiffness model of Shadmehr and Mussa-Ivaldi\cite{shadmehr1994adaptive} (Experiment 1) or a reduced stiffness (Experiment 2) to explore any dependence of reaching stiffness or accuracy on this assumption. The white noise force disturbance was designed to be unpredictable in order to minimize any effect of learning.}
\label{Yplots}
\end{figure}

\begin{figure}[t]
\centering
\framebox{\parbox{3in}{\includegraphics{error.eps}
}}
\caption{Subjects' reaching accuracy depended on the presence of force disturbance and the contents of visual feedback (A). Maximum deviation from straight-line reaching calculated during the first 250 milliseconds after the onset of movement revealed that turbulent force disturbance degraded reaching performance in both hand (B) and intent (C). Comparisons within treatment conditions revealed a significant advantage for the hand when force disturbance is not present and a significant advantage for intent when feedback of intent was used during exposure to turbulent forces. Performance using intent during turbulence was significantly better than performance using the hand (D). Significance among comparisons is denoted by an asterisk. Error did not signficantly depend on the choice between Shadmehr and Mussa-Ivaldi's\cite{shadmehr1994adaptive} stiffness model (experiment 1, blue) or a reduced stiffness (experiment 2, red) to determine intent.}
\label{error}
\end{figure}

\subsection*{Reaching Accuracy}
Even if subjects were capable of performing a reaching task using their estimated intent, a poor estimate would have lead to poor performance. Indeed, the hand significantly outperformed our intent estimate when the force disturbance is not present in block 1 (Figure 2D). Model and sensor inaccuracies degrade performance and result in an error of approximately 5 millimetres. In the presence of a force disturbance in block 2, the hand loses its advantage as model and sensor inaccuracies are balanced by some degree of cancellation of the disturbance. In block 3 where visual feedback of the intent is given instead of hand, the intent significantly outperforms the hand. For this intent estimate to be useful, subjects should perform better when using feedback of the intent than when using feedback of the hand. Comparing the hand's performance in block 2 to the intent's performance in block 3, subjects performed significantly better using their estimated intent. Finally, no significant differences were present across the two experiments. Performance was relatively insensitive to this change in the stiffness model used to deduce the intent.

\subsection*{Endpoint Stiffness}
While accuracy is desirable, it can be attained by co-contracting muscles to increase arm stiffness at the cost of metabolic effort \citep{gribble2003role, takahashi2001impedance}. Subjects stiffened significantly in response to white noise forces as seen by comparing stiffness in blocks 1 and 2 (Figure 3C). Subjects' stiffness significantly decreased when feedback of the deduced intent replaced feedback of the hand, as seen by comparing blocks 2 and 3. This decrease does not return stiffness to undisturbed levels, and it remains even after feedback of the hand resumes as seen by comparing blocks 3 and 4. Stiffness may have decreased with duration of exposure to uncertain disturbances\citep{takahashi2001impedance}. Subjects did not appear to have adjusted their stiffness to match the stiffness used in the estimation as subject and model stiffnesses were significantly different in experiment 2.

\begin{figure}[t]
\centering
\framebox{\parbox{3in}{\includegraphics{stiffness.eps}
}}
\caption{Subjects' arm stiffness depended on the presence of force disturbance and the contents of visual feedback (A). Arm stiffness calculated by linear regression during the first 250 milliseconds after the onset of movement revealed that turbulent force disturbance increased arm stiffness (B). Comparisons between treatment conditions revealed that exposure to turbulent forces caused by arm to stiffen significantly, but feedback of intent could significantly reduce this increase (C). Stiffness did not signficantly depend on the choice between Shadmehr and Mussa-Ivaldi's\cite{shadmehr1994adaptive} stiffness model (experiment 1, blue) or a reduced stiffness (experiment 2, red) to determine intent.}
\label{stiffness}
\end{figure}

@@

Although exposure to random forces damaged subjects’ reaching accuracy and increased their arm stiffness, replacing the veridical feedback with IF alleviated accuracy and stiffness. While other visual distortions typically degrade performance and require an adaptation period to overcome, IF immediately enhances performance. The simplest explanation for this is that IF approximates a signal already known to the brain: the path planned for the hand. In addition to its promise in performance enhancement, IF represents a novel means of revealing and studying the mechanisms of planning and control.

While IF alleviated the increased stiffness caused by exposure to random forces, stiffness remained significantly above baseline levels. Many explanations are reasonable. In particular, we might have hypothesized that the stiffness model used to determine intent might bias a person's arm stiffness, but the data did not support this conclusion. Alternatively, we might hypothesize that inaccuracy and incompleteness of the models used results in an estimate of intent that less accurate than subjects might desire. Since noise and performance inaccuracy can both be addressed by co-contraction, this may account for the remaining additional stiffness. Finally, it is possible that subjects co-contracted simply to counteract any residual perceived instability due to our slight lag in processing and presenting feedback.

Specific planned state trajectory even in the absence of explicit kinematic constraints.

Of particular scientific interest, "strict invariant" which has been described as opposite optimal feedback control.

Stiffness decreased, which provides secondary evidence of lower instability and unpredictability. Well, maybe it's just because of the numbers we chose. If we crank them down, can we get the stiffness even lower? Not so much. So clearly getting the stiffness right is very important.
In the absence of disturbing forces, estimated intent accuracy was lower than
that of the hand, which suggests the need for model improvements.

 The simplest explanation for this is that IF approximates a signal already known to the brain: the path planned for the hand. If so, IF r Moreover, this immediate performance enhancement during human-machine interaction implies a means by which robots can productively interact with a human without impeding them.

While this is pretty awesome, getting the stiffness right is an enormous limitation. Moreover, the stiffness model breaks down in the vicinity of the target for reasons unknown. The nature of control might be changing there and if so, we don't really know the specifics, but Shapiro has something to say about this.

Overall, this is something of a breakthrough

@@

The statement about the authors and contributors can be up to several sentences long, describing the tasks of individual authors referred to by their initials and should be included at the end of the manuscript before the References section.

\section*{Acknowledgments}
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text. Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.

\paragraph{Funding\textcolon} Text Text Text Text Text Text  Text Text.

\section*{Supplemental Data}
Supplementary Material should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder

Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.

%\bibliographystyle{frontiersinSCNS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
\bibliography{paper2.bib}

@@

>>>>

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Horowitz {et~al.}} %use et al only if is more than 1 author
\def\Authors{Justin Horowitz\,$^1$, Tejas Madhavan\,$^1$, Christine Massie\,$^1$ and James Patton\,$^{1,2,*}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Neuro-Machine Interaction Laboratory, University of Illinois at Chicago, Bionengineering, Chicago, Illinois, United States of America \\
$^{2}$Robotics Lab, Rehabilitation Institute of Chicago, Sensory Motor Performance Program, Chicago, Illinois, United States of America }
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{James Patton}
\def\corrAddress{Neuro-Machine Interaction Laboratory, University of Illinois at Chicago, Bionengineering, 851 S. Morgan Street, Chicago, Illinois, 60607-7052, United States of America}
\def\corrEmail{pattonj@uic.edu}

@@

In contrast, displaying anything other than what truthfully happens is a distortion and a lie. Like many other visual distortion experiments \citep{miles1980long, pine1996learning}, intent feedback (IF) introduces a visuomotor discrepancy that may be confusing to the nervous system. Preplanning a specific route may not necessary, and instead the system might continuously react to the environmental disturbances until it reaches the goal. If people try to achieve a goal while minimizing some measure of cost, it is possible to compute a set of rules for reacting to the environment without a specific intended route using optimal feedback control \citep{todorov2002optimal}. While this modeling strategy has been very successful at explaining data, it fundamentally assumes that corrective actions will be taken in response to relevant disturbances. Goals can also be reached at minimal \textit{expected} cost by constructing -- and possibly updating -- a specific intended route. IF may be troublesome if the nervous system cannot recognize it because no particular trajectory was intended.

@@

\subsection{Intent Extraction}
The well-known motion control structure of \cite{shadmehr1994adaptive} relates arm trajectory, $q$, to desired arm trajectory, $q_d$, and any external disturbance, $E$ using physical parameters of the arm. To show how this model can be algebraically inverted to instead describe desired arm trajectory as a function of arm trajectory and external disturbance, we write it as a torque balance:
\begin{equation}
\underbrace{\overbrace{M(q)\ddot{q}}^{\text{Inertia}}+\overbrace{G(q,\dot{q})}^{\text{Coriolis, Centripal}}}_{\text{Plant}}+E=
\underbrace{\overbrace{\tau_{ff}}^{\text{Feedforward}}+\overbrace{\tau_{fb}}^{\text{Feedback}}}_\text{Controller}
\end{equation}
Where $M$ is the mass matrix, $q$ is the joint angles, $\dot{q}$ is joint angular velocities, $\ddot{q}$ is joint angular accelerations, and $G$ contains both Coriolis and centripetal effects. Typical applications solve this torque balance for $\ddot{q}$ and use a numerical differential equation solver to predict arm trajectory in the context of a disturbance of interest, a feedback model, and feedforward torques determined by inverse dynamics. Rather than test hypotheses regarding the learning, production, or composition of this feedforward torque, we instead solve for it:
\begin{equation}
\tau_{ff}=M(q)\ddot{q}+G(q,\dot{q})+E-\tau_{fb}
\end{equation}
Then we note that feedforward torque can have a one-to-one correspondence with desired acceleration, $\ddot{q}_d$:
\begin{equation}
\hat{M}(q_d)\ddot{q}_d+\hat{G}(q_d,\dot{q}_d)+\hat{E}=\tau_{ff}
\end{equation}
Hats ( $\hat{}$ ) denote the nervous system's best estimate of a physical quantity. Combining these expressions, suppressing state dependencies, and solving for $\ddot{q}_d$:
\begin{equation}
\ddot{q}_d=\hat{M}^{-1} \{M\ddot{q}+G-\hat{G}+E-\hat{E}-\tau_{fb}\}
\end{equation}
In this form, a differential equation solver can determine $q_d$ as it evolves in time if a few assumptions are made and conditions are met. First, $\hat{E}$ must be modeled or assumed, so we choose $\hat{E}=0$. In the presence of a zero mean white noise force disturbance its mean should be zero, but it is unlikely to be exactly zero and may reflect an average of only the last few exposures \citep{scheidt2001learning}. Next, the matrix $\hat{M}(q_d)$ must be invertible, but we can ensure this through our choice of workspace. Finally, feedback torque requires a model of arm impedance, which is known to be task-dependent \citep{gomi1998task} and may vary over the course of a reach \citep{niu2010temporal}. With no prior knowledge of arm impedance for this task-disturbance combination, we presumed the feedback torque model of Shadmehr and Mussa-Ivaldi anticipating that it is sufficiently accurate or easy to learn (experiment 1). The experiment was repeated with a lower stiffness estimate (experiment 2) to explore any dependence on this assumption.

@@

\begin{figure}[h]
\centering
\framebox{\parbox{3in}{\includegraphics{Yplots.eps}
}}
\caption{Typical subjects made center-out targeted reaching motions under experimentally varied force and feedback conditions. Subjects used feedback of either hand motions (black lines) or estimated intent (red lines) to complete these reaches. Intent was estimated using either the stiffness model of \cite{shadmehr1994adaptive} (Experiment 1) or a reduced stiffness (Experiment 2) to explore any dependence of reaching stiffness or accuracy on this assumption. The white noise force disturbance was designed to be unpredictable in order to minimize any effect of learning.}
\label{Yplots}
\end{figure}

\begin{figure}[t]
\centering
\framebox{\parbox{3in}{\includegraphics{error.eps}
}}
\caption{Subjects' reaching accuracy depended on the presence of force disturbance and the contents of visual feedback (A). Maximum deviation from straight-line reaching calculated during the first 250 milliseconds after the onset of movement revealed that turbulent force disturbance degraded reaching performance in both hand (B) and intent (C). Comparisons within treatment conditions revealed a significant advantage for the hand when force disturbance is not present and a significant advantage for intent when feedback of intent was used during exposure to turbulent forces. Performance using intent during turbulence was significantly better than performance using the hand (D). Significance among comparisons is denoted by an asterisk. Error did not signficantly depend on the choice between stiffness model of \cite{shadmehr1994adaptive} (experiment 1, blue) or a reduced stiffness (experiment 2, red) to determine intent.}
\label{error}
\end{figure}

\subsection*{Reaching Accuracy}
Even if subjects were capable of using IF to perform a reaching task, a poor estimate would have lead to poor performance. Indeed, the hand significantly outperformed our intent estimate when the force disturbance is not present in block 1 (Figure 2D). Model and sensor inaccuracies degrade performance and result in an error of approximately 5 millimetres. In the presence of a force disturbance in block 2, the hand loses its advantage as model and sensor inaccuracies are balanced by some degree of cancellation of the disturbance. In block 3 where visual feedback of the intent is given instead of hand, the intent significantly outperforms the hand. For this intent estimate to be useful, subjects should perform better when using feedback of the intent than when using feedback of the hand. Comparing the hand's performance in block 2 to the intent's performance in block 3, subjects performed significantly better using their estimated intent. Finally, no significant differences were present across the two experiments. Performance was relatively insensitive to this change in the stiffness model used to deduce the intent.

\subsection*{Endpoint Stiffness}
While accuracy is desirable, it can be attained by co-contracting muscles to increase arm stiffness at the cost of metabolic effort \citep{gribble2003role, takahashi2001impedance}. Subjects stiffened significantly in response to white noise forces as seen by comparing stiffness in blocks 1 and 2 (Figure 3C). Subjects' stiffness significantly decreased when using IF replaced the hand position as their cursor, as seen by comparing blocks 2 and 3. This decrease does not return stiffness to undisturbed levels, and it remains even after feedback of the hand resumes as seen by comparing blocks 3 and 4. Stiffness may have decreased with duration of exposure to uncertain disturbances \citep{takahashi2001impedance}. Subjects did not appear to have adjusted their stiffness to match the stiffness used in the estimation as subject and model stiffnesses were significantly different in experiment 2.

@@

Although exposure to random forces hindered subjects’ reaching accuracy and increased their arm stiffness, replacing the veridical feedback with IF improved accuracy and decreased stiffness. While other visual distortions typically degrade performance and require an adaptation period to overcome, IF immediately enhanced performance. The performance variability inherent in white noise force disturbances complicates observation of learning, but there were no obvious differences in performance between the first and final exposures to IF.The simplest explanation for this is that IF approximates a signal already known to the brain: the path planned for the hand. In addition to its promise in performance enhancement, IF represents a novel means of revealing and studying the mechanisms of motor planning and motor control.

While IF alleviated the increased stiffness caused by exposure to random forces, stiffness remained significantly above baseline levels. Many explanations are reasonable. In particular, we might have hypothesized that subjects would adapt their own arm stiffness to decrease conflict with the stiffness model used to estimate their intent and thereby increase the accuracy of the estimate, but the data did not support this conclusion. Alternatively, inaccuracy and incompleteness of the models used might have resulted in an estimate of intent less accurate than subjects might desired. Since noise and performance inaccuracy can both be addressed by co-contraction, this may account for the residual stiffness. Finally, as subjects were not cued regarding the onset or removal of IF, the residual co-contraction may have been a precaution against the resumption of veridical feedback.

The ease with which subjects could make use of their estimated intent provides strong preliminary evidence that a specific intended trajectory is computed for the hand even when reaching in a highly variable environment. While recent work has identified kinematic constraints unnecessary for a task \citep{mistry2013optimal}, this is the first direct evidence that the entire trajectory is controlled even in the absence of specific instructions or constraints. It remains unclear when the intended trajectory is computed, but variability in the desired trajectory in phases 2 and 4 suggests that the trajectory is planned or at least can be replanned mid-movement. Certainly, it is not finalized before the onset of movement and is not a "strict invariant."

IF can facilitate human-machine collaboration and artificial performance augmentation by enabling the machine to preserve an operator's intent while cancelling unexpected disturbances from the environment. This would reduce the demand on the human operator and increase performance -- especially in environments with rapidly changing conditions. This assistance goes beyond environment cancellation by also accounting for any errors the operator might make based on their expectation of disturbance.

While IF holds tremendous promise, it also has strong limitations. IF is entirely dependent on the accuracy of the models used. While we were able to leverage measurements of cadaver anthropometrics, average tendencies do not capture individual variability. Similarly, the stiffness model of \cite{shadmehr1994adaptive} appears to have accurately captured the mean tendency (figure 3, bottom left) without accounting for variation among individuals or variation over time. Techniques that could estimate stiffness trajectories, perhaps even in real-time, would greatly increase the accuracy and utility of IF.

IF benefited subjects moving in a changing, uncertain environment. In addition to increasing subjects' accuracy, IF may have allowed subjects to reach their goals with less effort as arm stiffness decreased. While IF is limited by the accuracy of the models used, many candidate models are available and may outperform the simple model we investigated here. IF provides a novel form of feedback that may facilitate new insights into the nature of motor control and allows a machine to collaborate more effectively with a human user.

@@

All authors designed the work, analyzed the data, drafted and revised the manuscript, approved the final version, and agree to be held accountable for all aspects. TM and CM collected the data.

\section*{Acknowledgments}
The authors wish to thank Yazan Abdel Majeed for his review of the preliminary manuscript. We also thank the community  of the Robotics Lab at the Rehabilitation Institute of Chicago for critical commentary during the genesis of this paper and the work leading up to it.

\paragraph{Funding\textcolon} Funded By NIH R01-NS053606 and NIDRR H133E120010.

\bibliographystyle{frontiersinSCNS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
\bibliography{paper2.bib}

@@

\begin{figure}[t]
\centering
\framebox{\parbox{3in}{\includegraphics{stiffness.eps}
}}
\caption{Subjects' arm stiffness depended on the presence of force disturbance and the contents of visual feedback (A). Arm stiffness calculated by linear regression during the first 250 milliseconds after the onset of movement revealed that turbulent force disturbance increased arm stiffness (B). Comparisons between treatment conditions revealed that exposure to turbulent forces caused by arm to stiffen significantly, but feedback of intent could significantly reduce this increase (C). Stiffness did not signficantly depend on the choice between the stiffness model of \cite{shadmehr1994adaptive} (experiment 1, blue) or a reduced stiffness (experiment 2, red) to determine intent.}
\label{stiffness}
\end{figure}
